Ultra-deep $K_s$-band Imaging of the \textit{Hubble} Frontier Fields

### 2015-09-25 Paper0/ms.tex
test changed text.
test change.
edits to introduction

\author{Gabriel B. Brammer\altaffilmark{1},
et~al.}
% Pieter G.\ van Dokkum\altaffilmark{2},
% Garth D.\ Illingworth\altaffilmark{4},
% Rychard J.\ Bouwens\altaffilmark{3},
% Ivo Labb\'e\altaffilmark{3}, 
% Marijn Franx\altaffilmark{3},
% Ivelina Momcheva\altaffilmark{2},
% Pascal A.\ Oesch\altaffilmark{4}}
% Rub\'en S\'anchez-Janssen\altaffilmark{1}, 
% Ivo Labb\'e\altaffilmark{2},
% Elisabete da Cunha\altaffilmark{3},
% Dawn K.\ Erb\altaffilmark{4},
% Marijn Franx\altaffilmark{2},
% Mattia Fumagalli\altaffilmark{2},
% Britt Lundgren\altaffilmark{5},
% Danilo Marchesini\altaffilmark{6},
% Ivelina Momcheva\altaffilmark{5},
% Erica Nelson\altaffilmark{5},
% Shannon Patel\altaffilmark{2},
% Ryan Quadri\altaffilmark{7},
% Hans-Walter Rix\altaffilmark{3},
% Rosalind E.\ Skelton\altaffilmark{5},
% Kasper B.\ Schmidt\altaffilmark{3},
% Arjen van der Wel\altaffilmark{3},
% Pieter G.\ van Dokkum\altaffilmark{5},
% David A.\ Wake\altaffilmark{5},
% Katherine E.\ Whitaker\altaffilmark{5}}

@@

\altaffiltext{1}{ESA/AURA, Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
% \altaffiltext{2}
% {Department of Astronomy, Yale University, New Haven, CT 06520, USA}
% \altaffiltext{3}
% {Leiden Observatory, Leiden University, NL-2300 RA Leiden, Netherlands}
% \altaffiltext{4}
% {UCO/Lick Observatory, University of California, Santa Cruz, CA 95064}
% \altaffiltext{3}
% {Max Planck Institute for Astronomy (MPIA), K\"onigstuhl 17,
% 69117, Heidelberg, Germany}
% \altaffiltext{4}
% {Department of Physics, University of Wisconsin-Milwaukee, P.O. Box 413,
% Milwaukee, WI 53201, USA}
% \altaffiltext{5}
% {Department of Astronomy, Yale University, New Haven, CT 06520, USA}
% \altaffiltext{6}
% {Physics and Astronomy Department, Tufts University, Robinson Hall,
% Room 257, Medford, MA, 02155, USA}
% \altaffiltext{7}
% {Carnegie Observatories, 813 Santa Barbara Street, Pasadena, CA 91101, USA}

@@

Selecting in the reddest band possible.

K-band surveys:  ISAAC \citep{labbe:03}, NMBS, UltraVISTA, ...

Subaru Super Deep Field (AO) \cite{minowa:05}.

HUGS \citep{hugs}.

Frontier Fields

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Number counts figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\epsscale{1.18}
\plotone{number_counts_all.pdf} % Figures/exposure_map.pdf
\caption{Number counts.\label{fig:counts}}  
\end{figure*}

>>>>

\author{Gabriel B. Brammer\altaffilmark{1},
Danilo Marchesini\altaffilmark{2},
et~al.}
% Pieter G.\ van Dokkum\altaffilmark{2},
% Garth D.\ Illingworth\altaffilmark{4},
% Rychard J.\ Bouwens\altaffilmark{3},
% Ivo Labb\'e\altaffilmark{3}, 
% Marijn Franx\altaffilmark{3},
% Ivelina Momcheva\altaffilmark{2},
% Pascal A.\ Oesch\altaffilmark{4}}
% Rub\'en S\'anchez-Janssen\altaffilmark{1}, 
% Ivo Labb\'e\altaffilmark{2},
% Elisabete da Cunha\altaffilmark{3},
% Dawn K.\ Erb\altaffilmark{4},
% Marijn Franx\altaffilmark{2},
% Mattia Fumagalli\altaffilmark{2},
% Britt Lundgren\altaffilmark{5},
% Ivelina Momcheva\altaffilmark{5},
% Erica Nelson\altaffilmark{5},
% Shannon Patel\altaffilmark{2},
% Ryan Quadri\altaffilmark{7},
% Hans-Walter Rix\altaffilmark{3},
% Rosalind E.\ Skelton\altaffilmark{5},
% Kasper B.\ Schmidt\altaffilmark{3},
% Arjen van der Wel\altaffilmark{3},
% Pieter G.\ van Dokkum\altaffilmark{5},
% David A.\ Wake\altaffilmark{5},
% Katherine E.\ Whitaker\altaffilmark{5}}

@@

\altaffiltext{1}{ESA/AURA, Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
\altaffiltext{2}{Physics and Astronomy Department, Tufts University, Medford, MA, 02155, USA}
% \altaffiltext{6}
% {Department of Astronomy, Yale University, New Haven, CT 06520, USA}
% \altaffiltext{3}
% {Leiden Observatory, Leiden University, NL-2300 RA Leiden, Netherlands}
% \altaffiltext{4}
% {UCO/Lick Observatory, University of California, Santa Cruz, CA 95064}
% \altaffiltext{3}
% {Max Planck Institute for Astronomy (MPIA), K\"onigstuhl 17,
% 69117, Heidelberg, Germany}
% \altaffiltext{4}
% {Department of Physics, University of Wisconsin-Milwaukee, P.O. Box 413,
% Milwaukee, WI 53201, USA}
% \altaffiltext{5}
% {Department of Astronomy, Yale University, New Haven, CT 06520, USA}
% \altaffiltext{7}
% {Carnegie Observatories, 813 Santa Barbara Street, Pasadena, CA 91101, USA}

@@

During the last two decades, near-infrared (NIR) imaging has gained a dominant role in studies of galaxy formation and evolution.

Detection of galaxies in the $K$-band ($\lambda_{\rm eff} \sim 2.2$~$\mu$m) provided the first opportunity to construct a comprehensive picture of the population of galaxies in the early universe, as it enabled the discovery of galaxies at $z > 2$ with suppressed emission in the optical (i.e., rest-frame UV) due to evolved stellar populations and/or significant amount of dust extinction (e.g., \textcolor{red}{refs}). In fact, these galaxies, which dominate the high-mass end of the high-$z$ galaxy population, were previously missed by rest-frame UV selection techniques (e.g., $U$-dropout galaxies; \textcolor{red}{refs}). Imaging in the $K$-band allows for the direct probing out to $z\approx5$ of rest-frame wavelengths longer than the Balmer break. Sampling the rest-frame optical wavelength regime is crucial for high-$z$ studies, as significantly less affected by dust obscuration and a better probe of the galaxy stellar mass compared to the rest-frame UV (more sensitive to unobscured star formation). While imaging at even longer wavelengths ($\lambda>3$~$\mu$m) are needed to probe the rest-frame optical of galaxies in the first billion years of cosmic history, deep sub-arsec resolution imaging at these wavelengths will not be available until the advent of the {\it James Webb Space Telescope} ({\it JWST}). Deep $K$-band data with good enough (i.e., FWHM$<1^{\prime \prime}$) image quality have been fundamental to fully exploit {\it Spitzer}-IRAC imaging data characterized by much poorer spatial resolution, allowing for the correction of the resulting blending of sources in IRAC images. Finally, for space-based studies, $K$ band crucially fills the gap between the reddest {\it Hubble Space Telescope} ({\it HST}) filter (i.e., F160W, with $\lambda \sim 1.6$~$\mu$m) and the IRAC 3.6~$\mu$m pass-band, greatly improving the constraints on both the redshifts and the stellar-population properties of galaxies.

It is not surprising that, given the aforementioned reasons, all successful extragalactic surveys performed in the last fifteen years to investigate galaxies populations in the early universe invested significant resources to obtain deep NIR imaging data with good image quality, especially in the $K$ band, usually adopted as the detection band. Indeed, our understanding of galaxy formation and evolution in the last couple of decades has impressively proceeded forward mostly driven by NIR progressively deeper, wider, and with better image quality, surveys, such as ...  FIRES, FIREWORKS, NMBS, UltraVISTA, etc... Subaru Super Deep Field (AO) \cite{minowa:05}... HUGS \citep{hugs}.\textcolor{red}{-- we should provide a complete list of NIR surveys here -- }

The latest effort to further our knowledge of galaxy formation and evolution is represented by the HST Frontier Fields program. \textcolor{red}{-- brief description of HFF, followed by the need for mega-deep K-band data --}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Number counts figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\epsscale{1.18}
\plotone{number_counts_all.pdf} % Figures/exposure_map.pdf
\caption{$K_s$-band number counts in the Frontier Fields. \label{fig:counts}}  
\end{figure*}
